\problemname{Weather Report}

\illustration{0.4}{rain}{}%
You have been hired by the Association for Climatological Measurement, a
scientific organization interested in tracking global weather trends over a
long period of time.  Of course, this is no easy task.  They have deployed
many small devices around the world, designed to take periodic
measurements of the local weather conditions.
%
These are cheap devices with somewhat restricted capabilities.
Every day they observe which of the four standard kinds of weather occurred:
\emph{Sunny}, \emph{Cloudy}, \emph{Rainy}, or \emph{Frogs}.  After every $n$ of
these observations have been made, the results are reported to the
main server for analysis.
%
However, the massive number of devices
has caused the available communication bandwidth to be overloaded.
%have been overloading the available communication bandwidth.
The Association
needs your help to come up with a method of compressing these reports into
fewer bits.

For a particular device's location, you may assume that the weather
each day is an independent random event, and you are given the
predicted probabilities of the four 
possible weather types. Each of the $4^n$ possible weather reports for a
device must be encoded as a unique sequence of bits, such that no
sequence is a prefix of any other sequence (an important property, or
else the server would not know when each sequence ends). The goal
is to use an encoding that minimizes the expected number of
transmitted bits.


\section*{Input}
The first line of input contains an integer $1 \le n \le 20$,
the number of observations that go into each report.
%
The second line contains
four positive floating-point numbers,
$p_{\text{sunny}}$, $p_{\text{cloudy}}$,
$p_{\text{rainy}}$, and $p_{\text{frogs}}$,
representing the respective weather probabilities.
These probabilities have at most 6~digits after the decimal point and
sum to~1.

\section*{Output}
Display the minimum expected number of bits in the encoding of a report, with an
absolute or relative error of at most $10^{-4}$.
